Predator clusters

### 2023-02-14 reports/04_pred_clus.qmd
Clean up cluster report

Following the methods of Dietrich et al. (2021), clustering analysis is restricted to species sighted near 5% or more of stations. This avoids granting undue leverage to rare species. `r n_distinct(predators_abundant$species)` species retained.

@@

total_stations <- n_distinct(zoop_sf$amlr.station)
predators_stations %>%
  group_by(amlr.station, species) %>% 
  summarize(count = sum(count), .groups = "drop") %>%
  group_by(species) %>%
  summarize(stations_present = n(),
            station_frac = stations_present / total_stations,
            .groups = "drop") %>%
  arrange(desc(station_frac))

@@

```{r}
#| label: predator_clusters
#| warning: false
#| column: screen
#| out-width: 100%
#| fig-width: 6
#| fig-dpi: 600

>>>>

Following the methods of Dietrich et al. (2021), clustering analysis is restricted to species sighted near 5% or more of stations. This avoids granting undue leverage to rare species. `r n_distinct(predators_abundant$species)` species retained (SNPT to MIWH).

@@

total_stations <- n_distinct(zoop_sf$amlr.station)
predators_stations %>%
  group_by(amlr.station, species) %>% 
  summarize(count = sum(count), .groups = "drop") %>%
  group_by(species) %>%
  summarize(stations_present = n(),
            station_frac = stations_present / total_stations,
            .groups = "drop") %>%
  arrange(desc(station_frac)) %>% 
  knitr::kable()

@@

```{r}
#| label: predator_clusters
